\section{Employment}

\cventry{2023 -- present}{Platform Engineer}{Snapp!}{Tehran, Iran}{}{}
\begin{itemize}
      \item Led the design and implementation of a scalable, microservice-based architecture for a delivery industry application,
            using \httpslink[\textbf{NATS}]{nats.io} as the primary message-passing system for more than 125 clients and delivering
            more that 300k messages per second.
      \item Setup \textbf{Machine learning pipelines} using classical and neural network algorithms on \textbf{Kubernetes}.
      \item Lunch and monitor Kubernetes pods launched periodically by \httpslink[\textbf{Airflow}]{airflow.apache.org} for data processing.
      \item Setup \httpslink[\textbf{Seldon}]{www.seldon.io} for Data scientists so they can serve they models easily and without getting help from Dev team.
      \item Deploy Kafka on Kubernetes using \httpslink[\textbf{Strimzi}]{https://strimzi.io/} operator and maintain it to handle 300k message per second.
      \item Deploy Airflow on Amazon Elastic Compute Cloud (\textbf{EC2}) instances and then use its Amazon Elastic Container Service (\textbf{ECS}) operator to run our jobs.
      \item Deploy NATS on Red Hat OpenShift Service on AWS (\textbf{ROSA})
            using its Helm chart to reduce costs by deprecating Amazon Simple Queue Service (\textbf{SQS}).
      \item Setup Spark on AWS using Amazon Elastic Map Reduce (\textbf{EMR}).
      \item Migrate our Push Notification service to use Amazon Simple Notification Service (\textbf{SNS})
      \item Mentoring teams for effective use of NATS and other messaging systems that exists in across companies and vendors.
      \item Actively managed and resolved over 5 critical incidents as an on-call during last 6 months.
      \item Demonstrated a passion for technology and a positive approach to work,
            while maintaining strong communication and collaboration skills with engineering
            and non-engineering stakeholders alike.
      \item Working with \textbf{Rust} to implement concurrent, safe and performant Kubernetes operator for forcing
            policies over NATS CRDs including streams and consumers.
\end{itemize}

\vspace{0.5cm}

\cventry{2020 -- 2023}{Software Engineer}{Snapp!}{Tehran, Iran}{}{}
\begin{itemize}
      \item Optimized driver location collector (written in PHP) by migrating it into a modern platform, re-written in Go and cloud infrastructure,
            increasing availability by 20\% and facilitating faster rollout of new functionalities.
      \item Developed a \textbf{real-time stream processing} service to dynamically adjust pricing and balance demand and supply,
            resulting in a 5\% increase in the number of accepted rides.
      \item Developed and maintained backend services in \textbf{Golang} to ensure
            high \textbf{performance} and \textbf{reliability} for real-time order processing and \textbf{delivery tracking},
            and engineered a suite of \textbf{microservices} to enable real-time \textbf{geofencing} and in-memory geospatial
            indexing using \httpslink[\textbf{Tile38}]{tile38.com} with \textbf{sub-millisecond} response times.
      \item The team was responsible for user management, authentication and information security of users.
      \item Design \textbf{RESTFul} microservices for doing authentication, authorization and signup procedures which handles more 100k request per second.
      \item Re-write Golang projects to follow best practices like \textbf{DDD}, \textbf{SOLID}, etc.
      \item We designed a system for customer and courier number masking, developed it in \textbf{Golang} and deployed it on \textbf{OpenNebula} virtual machines.
      \item I migrated our services to \textbf{Kubernetes} on-promise cloud using \textbf{Helm} charts and \textbf{ArgoCD}.
      \item We used \httpslink[\textbf{ArgoCD}]{argo-cd.readthedocs.io/en/stable} ApplicationSet to automatically generate ArgoCD Application for our services and then we create \textbf{GitOps} pipeline for managing configuration and secrets in Git with their history available.
      \item I designed a system for automating the driver sign up process which reduced driver registration time to 15 minutes and increased the number of registered drivers.
      \item I fine tuned and deployed a pre-trained \textbf{OCR model} to read data from the social ID cards drivers uploaded in our drivers' sign up process. The model showed 92\% accuracy.
      \item Designed and optimized databases using \textbf{PostgreSQL} and \textbf{MongoDB},
        and implemented monitoring and alerting systems for real-time application observability using \textbf{OpenTelemetry}.
      \item Setup prototype validator based on \textbf{Envoy}'s \textbf{gRPC} interface. We use its gRPC interface to do the validation for incoming request
            based on headers, etc. Using this approach we could replace public keys in runtime.
      \item Mentoring Junior developers and help them to write clean, understandable and extendable code that scales well with the load.
      \item Setup CI/CD pipelines using GitLab CI.
\end{itemize}

\vspace{0.5cm}

\cventry{2018 -- 2020}{Software Engineer}{Avidnet Technology}{Tehran, Iran}{}{}
\begin{itemize}
      \item The goal of the team was to keep track of elderly people behavior with keeping their privacy.
      \item Used \textbf{Kalman filtering} to know where a person is.
      \item Keep track of the places a person spends time on a regular basis and name them.
      \item Predict where the person should be in a time bucket and alert otherwise.
      \item Used \textbf{Tensorflow Lite} to run the model on mobile phones.
      \item Setup a \textbf{Kafka} pipeline to gather data from sensors using \textbf{Protobuf} and then stores them into our \textbf{DataLake} (which is set up using \textbf{Postgres}).
      \item Make data compatible with GDPR before storing it.
      \item Draw the map of the house using accumulated GPS points
      \item Automatically make video calls with emergency contacts in case of abnormal behavior
      \item Provide in-application video call solution using WebRTC based on Pion Framework in Golang
      \item Setup turn server on AWS and use ELBs to open UDP/TCP ports
      \item Handle 1K concurrent calls based on our distributed design
      \item Setup project on Google Cloud Platform (\textbf{GCP}) Compute Engine using \textbf{Terraform}.
      \item Setup CI/CD pipelines using GitHub Actions.
      \item Helping the frontend team to develop related components using \textbf{Typescript} and \textbf{React}
\end{itemize}
