\section{Employment}

\cventry{Feb 2023 -- present}{Platform Engineer}{Snapp!}{Tehran, Iran}{}{}
\begin{itemize}
      \item Led the design and implementation of a scalable, microservice-based architecture for a delivery industry application,
            using \httpslink[\textbf{NATS}]{nats.io} as the primary message-passing system for more than 125 clients and delivering
            more that 300k messages per second.
      \item Setup \textbf{Machine learning pipelines} using classical and neural network algorithms on \textbf{Kubernetes}.
      \item Configure \httpslink[\textbf{Airflow}]{airflow.apache.org} pod operator for running job using pods periodically on SnappCloud.
      \item Setup \httpslink[\textbf{Seldon}]{www.seldon.io} for serving ML models which reduce their response time by 15\%
            with help of request batching and Protobuf protocol.
      \item Setup Google \textbf{Spark operator} on SnappCloud.
      \item Deploy Kafka on Kubernetes using \httpslink[\textbf{Strimzi}]{strimzi.io} operator and maintain it to handle 300k message per second.
      \item Deploy Airflow on Amazon Elastic Compute Cloud (\textbf{EC2}) instances and then use
            its Amazon Elastic Container Service (\textbf{ECS}) operator
            to run more than 100 jobs.
      \item Deploy NATS on Red Hat OpenShift Service on AWS (\textbf{ROSA})
            using its Helm chart to reduce costs 10\% by deprecating Amazon Simple Queue Service (\textbf{SQS}).
      \item Setup Spark on AWS using Amazon Elastic Map Reduce (\textbf{EMR}).
      \item Migrate our Push Notification service to use Amazon Simple Notification Service (\textbf{SNS})
      \item Mentoring 10 teams for effective use of NATS and other messaging systems that exists in across companies and vendors.
      \item Setup security, access management and control solutions using \textbf{Teleport} for around 10 services.
      \item Deployed recurrent pipelines to Kubernetes using \textbf{ArgoCD Workflow}
      \item Using \textbf{FastAPI} to serve more than 10 models for the data team and then deploy them on cloud.
      \item Working with \textbf{Rust} to implement concurrent, safe and performant Kubernetes operator for forcing
            policies over NATS CRDs including streams and consumers.
      \item Deploy \textbf{Cassandra} with 5 nodes on Virtual Machines to support teams that prefer availability over consistency.
      \item Setup \textbf{Avro Schema Registry} using Redpandas on SnappCloud
      \item Implemented exactly once semantics using \textbf{kafka stream} from topic to topic for 2 services.
      \item Demonstrated a passion for technology and a positive approach to work,
            while maintaining strong communication and collaboration skills with engineering
            and non-engineering stakeholders alike.
\end{itemize}

\vspace{0.5cm}

\cventry{Aug 2020 -- Feb 2023}{Software Engineer}{Snapp!}{Tehran, Iran}{}{}
\begin{itemize}
      \item Optimized driver location collector (written in \textbf{PHP}) by migrating it into a modern platform, re-written in \textbf{Go} and cloud infrastructure,
            increasing availability by 20\% and facilitating faster rollout of new functionalities.
      \item Developed a \textbf{real-time stream processing} service to dynamically adjust pricing and balance demand and supply,
            resulting in a 5\% increase in the number of accepted rides.
      \item Developed and maintained backend services in \textbf{Golang} to ensure
            high \textbf{performance} and \textbf{reliability} for real-time order processing and \textbf{delivery tracking},
            and engineered a suite of \textbf{microservices} to enable real-time \textbf{geofencing} and in-memory geospatial
            indexing using \httpslink[\textbf{Tile38}]{tile38.com} with \textbf{sub-millisecond} response times.
      \item Design \textbf{RESTFul} microservices for doing authentication, authorization and sign-up procedures which handles more 100k request per second.
      \item Re-write +2 Golang projects to follow best practices like \textbf{DDD}, \textbf{SOLID}, etc.
      \item We designed a system for customer and courier number masking, developed it in \textbf{Golang}
            and deployed it on virtual machines managed by \textbf{OpenNebula}. More than 30% of customers are using this feature.
      \item Migrated +20 of our services to \textbf{Kubernetes} on-promise cloud using \textbf{Helm} charts \textbf{andArgoCD}.
      \item We used \httpslink[\textbf{ArgoCD}]{argo-cd.readthedocs.io/en/stable} ApplicationSet to automatically generate ArgoCD Application
            for our services and then we create \textbf{GitOps} pipeline for managing configuration
            and secrets in Git with their history available.
      \item Designed a system for automating the driver sign up process which reduced driver registration time to 15 minutes and increased the number of registered drivers.
      \item Fine tuned and deployed a pre-trained \textbf{OCR model} to read data from the social ID cards drivers uploaded in our drivers' sign up process. The model showed 92\% accuracy.
      \item Designed and optimized databases using \textbf{PostgreSQL} and \textbf{MongoDB} which reduced response time of 3 services by 30\%,
            and implemented monitoring and alerting systems for real-time application observability using \textbf{OpenTelemetry}.
      \item Setup prototype validator based on \textbf{Envoy}'s \textbf{gRPC} interface. We use its gRPC interface to do the validation for incoming request
            based on headers, etc. Using this approach we could replace public keys in runtime.
      \item Setup CI/CD pipelines using \textbf{GitLab CI}.
      \item Mentoring Junior developers and help them to write clean, understandable and extendable code that scales well with the load.
\end{itemize}

\vspace{0.5cm}

\cventry{Jan 2018 -- Aug 2020}{Software Engineer}{Avidnet Technology}{Tehran, Iran}{}{}
\begin{itemize}
      \item The goal of the team was to keep track of elderly people behavior with keeping their privacy.
      \item Used \textbf{Kalman filtering} to know where a person is.
      \item Keep track of the places a person spends time on a regular basis and name them.
      \item Predict where the person should be in a 30 minute time bucket and alert otherwise.
      \item Used \textbf{Tensorflow Lite} to run the model on mobile phones.
      \item Setup a \textbf{Kafka} pipeline to gather data from sensors using \textbf{Protobuf} and
            then stores them into our \textbf{DataLake} (which is set up using \textbf{Postgres}) and can handle +20k messages per second.
      \item Make data compatible with GDPR before storing it.
      \item Draw the map of the house using accumulated GPS points
      \item Automatically make video calls with emergency contacts in case of abnormal behavior.
      \item Provide in-application video call solution using \textbf{WebRTC} based on \textbf{Pion} Framework in Golang.
      \item Setup turn server on AWS and use ELBs to open UDP/TCP ports
      \item Handle 1K concurrent calls based on our distributed design.
      \item Setup project on Google Cloud Platform (\textbf{GCP}) Compute Engine using \textbf{Terraform}.
      \item Setup CI/CD pipelines using \textbf{GitHub Actions}.
      \item Wrote web application using \textbf{Django} and Postgres for operational and support teams.
      \item Helping the frontend team to develop related components using \textbf{Typescript} and \textbf{React}
\end{itemize}
